---
title: "R Notebook"
output: html_notebook
---

```{r}
library(dplyr)
library(tidyr)
library(reshape2)
library(ggplot2)
library(lubridate)
```

extract quarter data 
```{r}
equity_month$month=substr(equity_month$date,6,7)
```

```{r}
# extract month
equity_quater=subset(equity_month, month=='01' | month=='04'| month=='07'| month=='10')
```
```{r}
# complete date
equity_quater$date=paste0(equity_quater$date,'-01')
```

```{r}
demo=data.frame(table(equity_quater$Stkcd))
names(demo)[1]='Stkcd'
demo=left_join(equity_quater,demo,by='Stkcd')
demo=subset(demo, Freq!=1)
```

```{r}
demo$date=paste0(demo$date,'-01')
demo$date=as.Date(demo$date,"%Y-%m-%d")
```
```{r}
demo1<-demo[order(demo$Stkcd,demo$date),]

```

Calulate quarter return
```{r}

demo1=demo1 %>% 
group_by(Stkcd) %>%
mutate(qReturn = Mon_p/lag(Mon_p) - 1)
```

##Financial statement
```{r}
sqldf('select count(distinct Stkcd) from Fstate')
table(month$substr.Fstate.Date..5..nchar.Fstate.Date..)
```

```{r}
bar=as.Date("1999-12-01",format="%Y-%m-%d")
Fstate=subset(Fstate, Date>=bar)
Fstate=subset(Fstate, Type=='A')
Fstate$month=substr(Fstate$Date,6,nchar(Fstate$Date))
Fstate=subset(Fstate, month!='01-01')
Fstate$Date=as.Date(Fstate$Date,"%Y-%m-%d")+10
Fstate$Date=as.character(Fstate$Date)
Fstate$Date=substr(Fstate$Date,1,nchar(Fstate$Date)-2)
Fstate$Date=paste0(Fstate$Date,'01')
Fstate$Date=as.Date(Fstate$Date,"%Y-%m-%d")
```


```{r}
Fstate$ID=paste0(Fstate$Stkcd,Fstate$Date)
table(duplicated(Fstate$ID))
```

```{r}
demo1$ID=paste0(demo1$Stkcd,demo1$date)
demo=left_join(demo1,Fstate[ , c("ID", "BE")], by = "ID", all.x=TRUE)
```
```{r}
table(duplicated(demo$ID))
```

fill na value with previous value
```{r}
demo=demo %>%
  group_by(Stkcd) %>%
  fill(BE, .direction = "down") %>%
  ungroup()
```

Design portfolios
```{r}
#demo2<-demo2[order(demo2$date),]
quantile=ddply(demo2, .(date), function(x) quantile(x$size,prob = seq(from =0, to=1, by=0.1)))
```

##winsorize 30% smallest##unfinished

Sort Size
```{r}
demo=demo %>%
  group_by(date) %>%
  mutate(qSize = ntile(size, 10))%>%
  ungroup()
```
Sort BE/BM
```{r}
demo2$BM=demo2$BE/demo2$size
demo=demo2 %>%
  group_by(date) %>%
  mutate(qBM = ntile(BM, 10))%>%
  ungroup()
demo2=demo
rm(demo)
```
FF25 portfolio
```{r}
demo=demo %>%
  group_by(date) %>%
  mutate(qSize5 = ntile(size, 5),qBM5 = ntile(BM, 5))%>%
  ungroup()
demo$FF5=paste0("SZ",demo$qSize5,"BM",demo$qBM5 )

demo$date=as.Date(demo$date,"%Y/%m/%d")
Preturn=demo %>%
  group_by(date,FF5) %>%
  summarise(Pqreturn = mean(qReturn))%>%
  ungroup()

```

```{r}
demo=filter(demo2,!is.na(qReturn))
```

```{r}
demo$Port=paste(demo$qBM,demo$qSize,sep='+')
demo=demo %>%
  group_by(date,Port) %>%
  mutate(Pqreturn=mean(qReturn))%>%
  ungroup()
```
```{r}
Preturn=demo %>%
  group_by(date,Port) %>%
  summarise(Pqreturn = mean(qReturn))


```
Count number
```{r}
write.csv(demo2,file='D:\\full_data.csv')
```

Year return data
```{r}
year_bond=subset(demo2, month=='01'|month=='07')
```
Calculate half-annual return
```{r}
library(dplyr)
year_bond<-year_bond[order(year_bond$Stkcd,year_bond$date),]

year_bond=year_bond %>% 
group_by(Stkcd) %>%
mutate(yReturn = Mon_p/lag(Mon_p) - 1) %>%
ungroup()
```
calculate portfolio return
```{r}
year_bond$Port=paste(year_bond$qBM,year_bond$qSize,sep='-')
year_demo=filter(year_bond,!is.na(yReturn))

Pyreturn=year_demo %>%
  group_by(date,Port) %>%
  summarise(Pyreturn = mean(yReturn))%>%
  ungroup()
```
```{r}
write.csv(year_bond,file = 'D:\\year_bond.csv')
write.csv(Pyreturn,file = 'D:\\Pyreturn.csv')
```

Bank Data
```{r}

broker_dealer_asset=melt(broker_dealer_asset,id.vars=c("Stkcd","name"),variable.name="date",value.name="asset")
broker_dealer_debt=melt(broker_dealer_debt,id.vars=c("Stkcd","name"),variable.name="date",value.name="debt")
```
```{r}

broker_dealer_asset$Stkcd=substr(broker_dealer_asset$Stkcd,1,nchar(broker_dealer_asset$Stkcd)-3)
broker_dealer_debt$Stkcd=substr(broker_dealer_debt$Stkcd,1,nchar(broker_dealer_debt$Stkcd)-3)
broker_dealer_asset$date=as.character(broker_dealer_asset$date)
broker_dealer_debt$date=as.character(broker_dealer_debt$date)
broker_dealer_asset$date=trimws(broker_dealer_asset$date,which = c("both"))
broker_dealer_debt$date=trimws(broker_dealer_debt$date,which = c("both"))
```
```{r}
broker_dealer_asset$ID=paste(broker_dealer_asset$Stkcd,broker_dealer_asset$date,sep='')
broker_dealer_debt$ID=paste(broker_dealer_debt$Stkcd,broker_dealer_debt$date,sep='')
broker_dealer=left_join(broker_dealer_asset,broker_dealer_debt %>% select(ID,debt) ,by='ID')
#commercial_bank=subset(commercial_bank, select = -c(d, b ) )
#bank=rbind(commercial_bank,state_bank)
```

```{r}
broker_tot=broker_dealer%>%
  group_by(date) %>%
  summarise(tot_asset= sum(asset, na.rm=T),tot_debt= sum(debt, na.rm=T))%>%
  ungroup()
```
Bank Data

```{r}

write.csv(broker_dealer,file='D:\\broker.csv')
write.csv(broker_tot,file='D:\\broker_sum.csv')
```

```{r}
broker_tot$date=as.Date(broker_tot$date,"%Y-%m-%d")

```
```{r}
#broker_tot
ggplot(bank_tot, aes(date, d_ratio)) + geom_line() + scale_x_date(date_breaks = "1 year", date_labels = "%y") +
  coord_cartesian(xlim = c(
    as.Date("2004-12-01", "%Y-%m-%d"),
    as.Date("2020-12-31", "%Y-%m-%d")
  ))

```
Bond data
```{r}
test1$Abbrnme=NULL
test1$Listdt=NULL
```

```{r}
library(sqldf)
dup=sqldf('select Liscd from bndinfo group by Liscd HAVING COUNT(1)>1')
```
```{r}
test1=inner_join(bndinfo,dup,by='Liscd')
```
```{r}
sqldf('select count(distinct Liscd) from bond_mth')
sqldf('select count(distinct Liscd) from bndinfo')
sqldf('select count(distinct Liscd) from bndinfo group by Sctcd')
```
```{r}
demo=sqldf('select * from bond_mth where Liscd="010004"')
```
```{r}
test_p=subset(bndinfo,Sctcd!="3")
bond=left_join(bond_mth,test_p,by='Liscd')
```
Test whether eliminate those info
```{r}
library(dplyr)
test_Na_num=bond %>% group_by(Liscd) %>%
  summarise(num_na=sum(is.na(Matdt)))
```
```{r}
demo_na=filter(bond,is.na(Matdt))
demo_na=demo_na[,1:3]
```
```{r}
demo_na=left_join(demo_na,bndinfo,by="Liscd")
```
remove na value
```{r}
bond=filter(bond,!is.na(Matdt))
colnames(bond)[2]="date"
```
```{r}
bond$date=paste0(bond$date,"-01-01")
bond$date=as.Date(bond$date,"%Y-%m-%d")
```
calculate maturity
```{r}
non_risk$date=as.Date(non_risk$date,"%Y-%m-%d")
demo=left_join(bond,non_risk,by="date")
demo$time_mat=demo$Matdt-demo$date
demo$spread=demo$qReturn-demo$rate
```

calculate quarter return
```{r}
demo$date=as.character(demo$date)
demo$month=substr(demo$date,6,7)
demo=subset(demo, month=='01' | month=='04'| month=='07'| month=='10')

demo$Matdt=as.Date(demo$Matdt,"%Y-%m-%d")
demo<-demo[order(demo$Liscd,demo$date),]
demo=demo %>% 
group_by(Liscd) %>%
mutate(qReturn = Mopnprc/lag(Mopnprc) - 1)

```


```{r}
gov_bond=subset(demo,Bndtype=="01"|Bndtype=="04")
cor_bond=subset(demo,Bndtype=="02"|Bndtype=="03")
```
```{r}
gov_bond=filter(gov_bond,!is.na(qReturn))
gov_bond=filter(gov_bond,qReturn!=Inf)
gov_bond=gov_bond %>%
  group_by(date) %>%
  mutate(qMature = ntile(time_mat, 5))%>%
  ungroup()
```
sort on spread
```{r}
cor_bond=filter(cor_bond,!is.na(qReturn)) 
cor_bond=filter(cor_bond,qReturn!=Inf)
cor_bond=cor_bond %>%
  group_by(date) %>%
  mutate(qSpread = ntile(spread, 20))%>%
  ungroup()
```
```{r}
write.csv(demo,file="D:\\bond_full.csv")
write.csv(gov_bond,file="D:\\gov_bond.csv")
write.csv(cor_bond,file="D:\\cor_bond.csv")
write.csv(port_gov,file="D:\\port_gov.csv")
write.csv(port_cor,file="D:\\port_cor.csv")
```

```{r}
port_gov=gov_bond %>%
  group_by(date,qMature) %>%
  summarise(return = mean(qReturn))%>%
  ungroup()
```
```{r}
port_cor=cor_bond %>%
  group_by(date,qSpread) %>%
  summarise(return = mean(qReturn))%>%
  ungroup()
```

Regression

```{r}
broker$name=NULL
broker$date=as.Date(broker$date,"%Y/%m/%d")
broker$date=broker$date+days(10)
broker$date=substr(as.character(broker$date),1,8)
broker$date=paste0(broker$date,"01")
broker$date=as.Date(broker$date,"%Y-%m-%d")

broker$mon = substr(as.character(broker$date), 6, 7)
broker$yrs = substr(as.character(broker$date), 1, 4)
broker_summary = broker %>% subset(mon == "01" | mon == "04") %>%
  group_by(date) %>% 
  summarise(tot_asset = sum(asset,na.rm=TRUE))%>%ungroup()
broker_summary$yrs=substr(as.character(broker_summary$date), 1, 4)

broker_summary%>%group_by(yrs)%>%arrange(date)%>%mutate(ratio=tot_asset/lag(tot_asset))%>%ungroup()

```
bank tot
```{r}
bank_test=bank%>%group_by(Stkcd,yrs)%>%mutate(sm=sum(debt))
bank_test=subset(bank_test,!is.na(sm))
bank_test=subset(bank_test,date>as.Date("2004-6-20","%Y-%m-%d"))

bank_tot=bank_test%>%group_by(date)%>%summarise(tot_asset=sum(asset),tot_debt=sum(debt),d_ratio=tot_debt/tot_asset)

bank_tot=bank_tot[order(bank_tot$date),]
bank_tot$lag_ratio=lag(bank_tot$d_ratio)

bank_tot=filter(bank_tot,!is.na(lag_ratio))
```

```{r}
broker_test=broker%>%group_by(Stkcd,yrs)%>%mutate(sm=sum(debt))
broker_test=subset(broker_test,!is.na(sm))
broker_test=subset(broker_test,date>as.Date("2004-6-20","%Y-%m-%d"))

broker_tot=broker_test%>%group_by(date)%>%summarise(tot_asset=sum(asset),tot_debt=sum(debt),d_ratio=tot_debt/tot_asset)

broker_tot=broker_tot[order(broker_tot$date),]
broker_tot$lag_ratio=lag(broker_tot$d_ratio)

broker_tot=filter(broker_tot,!is.na(lag_ratio))

delta=lm(d_ratio ~ lag_ratio, data = broker_tot)
broker_tot$delta_d=delta$residuals

Preturn_05$rate=Preturn_05$rate*0.01
```
```{r}
Preturn_05=subset(Preturn,date>as.Date("2004-6-20","%Y-%m-%d"))
demo=demo %>%group_by(date) %>%mutate(prop=size/sum(size))
Market_r=demo %>%
  group_by(date) %>%
  summarise(Wmrk = weighted.mean(qReturn,prop))%>%
  ungroup()

non_risk$date=as.Date(non_risk$date,"%Y-%m-%d")
Market_r=left_join(Market_r, non_risk, by='date')

Preturn_05=left_join(Preturn_05,Market_r)

Preturn_05=left_join(Preturn_05,broker_tot %>% select(date,delta_d),by='date')

Test_05=filter(Preturn_05,!is.na(delta_d))
```

Index market return
```{r}
mrk=subset(mrk,code=='000001')
mrk$y_m=substr(mrk$date,1,7)
mrk$date=as.Date(mrk$date,format = "%Y-%m-%d")
mrk=mrk[order(mrk$date),]
mrk=mrk%>%group_by(y_m)%>%filter(row_number()==1)

mrk$y_m=paste0(mrk$y_m,'-01')
mrk$y_m=as.Date(mrk$y_m,format = "%Y-%m-%d")

mrk$month=substr(mrk$date,6,7)
mrk=subset(mrk, month=='01' | month=='04'| month=='07'| month=='10')
mrk$mrk=(mrk$Index/lag(mrk$Index) - 1)

mrk$date=NULL
colnames(mrk)[which(names(mrk) == "y_m")] <- "date"
colnames(mrk)[which(names(mrk) == "mrk")] <- "Ind_mrk"

```

```{r}
Preturn_05$Pqreturn_exc=Preturn_05$Pqreturn-Preturn_05$rate
Preturn_05$mrk=Preturn_05$return-Preturn_05$rate
Test_05=filter(Preturn_05,!is.na(delta_d))
```

Bond market return
```{r}
bond_num$size=bond_num$price*bond_num$num
bond_num$month=substr(bond_num$date,6,7)
bond_num=subset(bond_num, month=='01' | month=='04'| month=='07'| month=='10')
bond_num$date=paste0(bond_num$date,'-01')
bond_num$date=as.Date(bond_num$date,format = "%Y-%m-%d")
bond_num=bond_num[order(bond_num$date),]
bond_num$qreturn=(bond_num$price/lag(bond_num$price) - 1)
```
```{r}
bond_num=filter(bond_num,!is.na(qreturn))
bond_num=filter(bond_num,qreturn!=Inf)
bond_num=bond_num %>%group_by(date) %>%mutate(prop=size/sum(size))
bond_mrk=bond_num %>%
  group_by(date) %>%
  summarise(Bmrk = weighted.mean(qreturn,prop))%>%
  ungroup()
```
```{r}
avg_mrk=demo %>%
  group_by(date) %>%
  summarise(ag_mrk = mean(Pqreturn))%>%
  ungroup()
Market_r=left_join(Market_r,avg_mrk,by="date")
```
```{r}
mrk_mon=subset(mrk_mon,type==1)
mrk_mon$month=substr(mrk_mon$date,6,7)
mrk_mon$quar=0
mrk_mon$quar[which(mrk_mon$month == "01"|mrk_mon$month == "02"|mrk_mon$month == "03")] ="04-01"
mrk_mon$quar[which(mrk_mon$month == "04"|mrk_mon$month == "05"|mrk_mon$month == "06")] ="07-01"
mrk_mon$quar[which(mrk_mon$month == "07"|mrk_mon$month == "08"|mrk_mon$month == "09")] ="10-01"
mrk_mon$quar[which(mrk_mon$month == "10"|mrk_mon$month == "11"|mrk_mon$month == "12")] ="12-30"

mrk_mon$y_q=paste0(substr(mrk_mon$date,1,4),'-',mrk_mon$quar)

mrk_mon_1=mrk_mon%>%group_by(y_q)%>%summarise(qreturn=sum(return))
```
```{r}
mrk_mon_1$date=as.Date(mrk_mon_1$y_q,format = '%Y-%m-%d')+days(10)
mrk_mon_1$date=substr(as.character(mrk_mon_1$date),1,7)
mrk_mon_1$date=as.Date(paste0(mrk_mon_1$date,'-01'),format = '%Y-%m-%d')
mrk_mon_1$y_q=NULL
```

```{r}
Preturn_05$Wmrk=NULL
Market_r=left_join(Market_r,bond_mrk,by="date")
Market_r=left_join(Market_r,mrk_mon_1,by="date")
```

```{r}
Preturn_05=left_join(Preturn_05,broker_tot%>%select(d_ratio,date),by='date')
```

```{r}
Market_r$mrk=(Market_r$qreturn+Market_r$Bmrk)/2-Market_r$rate
Test_05=filter(Preturn_05,!is.na(delta_d))
Test_05=left_join(Test_05,Market_r,by='date')
Test_05=Test_05[order(Test_05$FF5),]
fitted_models = Test_05 %>% group_by(FF5) %>% do(model = lm(Pqreturn ~ d_ratio+ag_mrk, data = .))

Belta=data.frame()
for (i in 1:25){
  tem=as.data.frame(summary(fitted_models$model[[i]])$coefficients)
  Belta=rbind(Belta,tem)
}
```
```{r}
B_ratio = data.frame (beta  = c(1), FF5 = c(2), mrk_b=c(3))
ind=0
for (i in 1:5) {
  for (j in 1:5) {
    ind=ind+1
    B_ratio[ind, 1] = summary(fitted_models$model[[ind]])$coefficients[2]
    B_ratio[ind, 2] = paste0("SZ",i,"BM",j)
     B_ratio[ind, 3] = summary(fitted_models$model[[ind]])$coefficients[3]
  }
}
```

```{r}
MF_return=Test_05 %>%
  group_by(FF5) %>%
  summarise(M_Freturn = mean(Pqreturn))%>%
  ungroup()

B_ratio=left_join(B_ratio,MF_return,by="FF5")
```
```{r}
p_risk=lm(M_Freturn~beta+mrk_b,data = B_ratio)
summary(p_risk)
```

Bank regression
```{r}
test=subset(bank_tot,!is.na(diff_res))
```
```{r}
Preturn_08=subset(Preturn,date>as.Date("2007-12-30","%Y-%m-%d"))
Preturn_08=left_join(Preturn_08,test,by="date")

```
```{r}
library(dplyr)
bank_reg = Preturn_08 %>% group_by(FF5) %>% do(model = lm(Pqreturn ~ d_ratio, data = .))
bank_model=data.frame()
for (i in 1:25){
  tem=as.data.frame(summary(bank_reg$model[[i]])$coefficients)
  bank_model=rbind(bank_model,tem)
}
```
#bond regression

```{r}
bond_full$date=as.Date(bond_full$date,format ="%Y/%m/%d")
port_cor$date=as.Date(port_cor$date,format = "%Y/%m/%d")
port_gov$date=as.Date(port_gov$date,format = "%Y/%m/%d")

bond_mrk=demo %>%
  group_by(date) %>%
  summarise(mrk = mean(qReturn))%>%
  ungroup()

non_risk$rate=0.01*non_risk$rate
bond_mrk=left_join(bond_mrk, non_risk, by='date')
port_cor=left_join(port_cor, bond_mrk, by='date')
port_gov=left_join(port_gov, bond_mrk, by='date')

gov_bond_05=subset(port_gov,date>as.Date("2004-6-20","%Y-%m-%d"))
cor_bond_05=subset(port_cor,date>as.Date("2004-6-20","%Y-%m-%d"))

```
```{r}
gov_bond_05=left_join(gov_bond_05,broker_tot %>% select(date,delta_d),by='date')
gov_bond_05=left_join(gov_bond_05,broker_tot %>% select(date,d_ratio),by='date')
cor_bond_05=left_join(cor_bond_05,broker_tot %>% select(date,d_ratio),by='date')
cor_bond_05=left_join(cor_bond_05,broker_tot %>% select(date,delta_d),by='date')
```

```{r}
gov_bond_05$mrk=NULL
gov_bond_05$Ind_mrk=NULL
gov_bond_05$exc_mrk=NULL
gov_bond_05=left_join(gov_bond_05,Market_r,by='date')
gov_bond_05=filter(gov_bond_05,!is.na(delta_d))
gov_bond_05=gov_bond_05[order(gov_bond_05$qMature),]
```

#cor_bond
```{r}
cor_bond_05$mrk=NULL

cor_bond_05=left_join(cor_bond_05,Market_r,by='date')
cor_bond_05=filter(cor_bond_05,!is.na(delta_d))
cor_bond_05=cor_bond_05[order(cor_bond_05$qSpread),]
```


```{r}
cor_bond_05=cor_bond_05[order(cor_bond_05$qSpread),]
cor_fitted_bond = cor_bond_05 %>% group_by(qSpread) %>% do(model = lm(return ~ d_ratio+ag_mrk, data = .))

cor_Beta=data.frame()
for (i in 1:20){
  tem=as.data.frame(summary(cor_fitted_bond$model[[i]])$coefficients)
  cor_Beta=rbind(cor_Belta,tem)
}
```
```{r}
gov_bond_05=cor_bond_05[order(gov_bond_05$qMature),]
gov_fitted_bond = gov_bond_05 %>% group_by(qMature) %>% do(model = lm(return ~ d_ratio+ag_mrk, data = .))

gov_Beta=data.frame()
for (i in 1:5){
  tem=as.data.frame(summary(gov_fitted_bond$model[[i]])$coefficients)
  gov_Beta=rbind(gov_Beta,tem)
}

bond_Beta=rbind(cor_Beta,gov_Beta)
```
```{r}
B_ratio_bond = data.frame (beta  = c(1), FF5 = c(2), mrk_b=c(3))
for (i in 1:5) {
    B_ratio_bond[i, 1] = summary(gov_fitted_bond$model[[i]])$coefficients[2]
    B_ratio_bond[i, 2] = paste0("gov",i)
}

for (i in 1:20) {
    ind=i+5
    B_ratio_bond[ind, 1] = summary(cor_fitted_bond$model[[i]])$coefficients[2]
    B_ratio_bond[ind, 2] = paste0("cor",i)

}
```

```{r}
MF_return=Test_05 %>%
  group_by(FF5) %>%
  summarise(M_Freturn = mean(Pqreturn))%>%
  ungroup()

B_ratio=left_join(B_ratio,MF_return,by="FF5")
```
```{r}
p_risk=lm(M_Freturn~beta+mrk_b,data = B_ratio)
summary(p_risk)

```


